### 2015-06-12 rapport/msp.tex
rapport_12_06

%====BIG EXAMPLE
\begin{figure}[ht!]
\begin{center}
% INITIAL GRAPH
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (c0) at (0,0) {$c_0$};
   \node[] (c1) at (1,0) {$c_1^*$};
   \node[] (c2) at (2,0.5) {$c_2$};
   \node[] (c3) at (2,-0.5) {$c_3$};
   \node[] (c4) at (3,0.5) {$c_4^*$};
   \node[] (c5) at (3,-0.5) {$c_5$};
   \node[] (c6) at (4,0.5) {$c_6$};
   \node[] (c7) at (5,0) {$c_7$};
   \node[] (c8) at (6,0) {$c_8^*$};

  \path[->]
    (c0) edge node {} (c1)
    (c1) edge node {} (c2)
         edge node {} (c3)
    (c2) edge node {} (c4)
    (c4) edge node {} (c6)
    (c3) edge node {} (c5)
    (c5) edge node {} (c7)
    (c6) edge node {} (c7)
    (c7) edge node {} (c8);
  \end{tikzpicture}
}
\\
% INVERSE LINE GRAPH
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c0d) at (1,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c2d) at (3,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c3d) at (3,-0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c7d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

  \path[->]
    (c0s) edge node [above] {$c_0$} (c0d)
    (c0d) edge node [above] {$c_1^*$} (c1d)
    (c1d) edge node [above] {$c_2$} (c2d)
          edge node [above] {$c_3$} (c3d)
    (c2d) edge node [above] {$c_4^*$} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {$c_7$} (c7d)
    (c7d) edge node [above] {$c_8$} (c8d)
    (c3d) edge node [above] {$c_5$} (c6d);
  \end{tikzpicture}
}
\\
% TRANSFORMATIONS
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c2d) at (3,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c3d) at (3,-0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   %\node[] (c8) at (6.5,1.5) {$c_8^*$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

  \path[->]
    (c0s) edge node {} (c1d)
    (c1d) edge node [above] {$c_2$} (c2d)
          edge node [above] {$c_3$} (c3d)
    (c2d) edge node [above] {$c_4^*$} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {} (c8d)
    (c3d) edge node [above] {$c_5$} (c6d)

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
        edge node {} (s2)
    (s2) edge node {} (star1)
        edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8);
        edge node {} (s4)
    (s4) edge node {} (star8)
        edge node {} (c8);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   %\node[] (c8) at (6.5,1.5) {$c_8^*$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

   %reduction c3 c5
   \node[] (s5) at (3.5,-2) {$\mathcal{S}$};
   \node[] (c3) at (3,-1) {$c_3$};
   \node[] (c5) at (4,-1) {$c_5$};

   %reduction c2 c4
   \node[] (s6) at (3.5,1) {$\mathcal{S}$};
   \node[] (c2) at (3,2) {$c_2$};
   %\node[] (c4) at (4,2) {$c_4^*$};
   \node[] (s7) at (4,2) {$\mathcal{S}$};
   \node[] (star4) at (3.5,3) {$*_4$};
   \node[] (c4) at (4.5,3) {$c_4$};

  \path[->]
    (c0s) edge node {} (c1d)
    (c1d) edge [bend left] node [above] {} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {} (c8d)
    (c1d) edge [bend right] node [above] {} (c6d)

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

@@

    %reduction c7 c8
    (s6) edge node {} (c2)
    %     edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}

\begin{figure}[ht!]
\ContinuedFloat
\begin{center}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   %\node[] (c8) at (6.5,1.5) {$c_8^*$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

   %reduction c3 c5
   \node[] (s5) at (3.5,-2) {$\mathcal{S}$};
   \node[] (c3) at (3,-1) {$c_3$};
   \node[] (c5) at (4,-1) {$c_5$};

   %reduction c2 c6
   \node[] (s8) at (3.5,1) {$\mathcal{S}$};
   \node[] (c6) at (4,2) {$c_6$};
   \node[] (s6) at (3,2) {$\mathcal{S}$};
   \node[] (c2) at (2.5,3) {$c_2$};
   %\node[] (c4) at (3.5,3) {$c_4^*$};
   \node[] (s7) at (3.5,3) {$\mathcal{S}$};
   \node[] (star4) at (3,4) {$*_4$};
   \node[] (c4) at (4,4) {$c_4$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

@@

    %reduction c2 c6
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
    %     edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (7,0.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,1.5) {$c_7$};
   %\node[] (c8) at (7.5,1.5) {$c_8^*$};
   \node[] (s4) at (7.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (7,2.5) {$*_8$};
   \node[] (c8) at (8,2.5) {$c_8$};

   %reduction c2 c4 c6 c3 c5
   \node[] (p1) at (4,0.5) {$\mathcal{P}$};
   \node[] (s5) at (3,1) {$\mathcal{S}$};
   \node[] (c3) at (2.5,2) {$c_3$};
   \node[] (c5) at (3.5,2) {$c_5$};
   \node[] (s8) at (5,1) {$\mathcal{S}$};
   \node[] (c6) at (5.5,2) {$c_6$};
   \node[] (s6) at (4.5,2) {$\mathcal{S}$};
   \node[] (c2) at (4,3) {$c_2$};
   %\node[] (c4) at (5,3) {$c_4^*$};
   \node[] (s7) at (5,3) {$\mathcal{S}$};
   \node[] (star4) at (4.5,4) {$*_4$};
   \node[] (c4) at (5.5,4) {$c_4$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

    %reduction c2 c4 c6 c3 c5
    (p1) edge node {} (s5)
         edge node {} (s8)
    (s5) edge node {} (c3)
         edge node {} (c5)
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
         %edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};

   %all
   \node[] (s9) at (2.5,1.5) {$\mathcal{S}$};
   \node[] (s10) at (4,0.5) {$\mathcal{S}$};

   %reduction c0 c1
   \node[] (s1) at (1,2) {$\mathcal{S}$};
   \node[] (c0) at (0.5,3) {$c_0$};
   \node[] (s2) at (1.5,3) {$\mathcal{S}$};
   \node[] (star1) at (1,4) {$*_1$};
   \node[] (c1) at (2,4) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (7,1) {$\mathcal{S}$};
   \node[] (c7) at (6.5,2) {$c_7$};
   \node[] (s4) at (7.5,2) {$\mathcal{S}$};
   \node[] (star8) at (7,3) {$*_8$};
   \node[] (c8) at (8,3) {$c_8$};

   %reduction c2 c4 c6 c3 c5
   \node[] (p1) at (4,2) {$\mathcal{P}$};
   \node[] (s5) at (3,2.5) {$\mathcal{S}$};
   \node[] (c3) at (2.5,3.5) {$c_3$};
   \node[] (c5) at (3.5,3.5) {$c_5$};
   \node[] (s8) at (5,2.5) {$\mathcal{S}$};
   \node[] (c6) at (5.5,3.5) {$c_6$};
   \node[] (s6) at (4.5,3.5) {$\mathcal{S}$};
   \node[] (c2) at (4,4.5) {$c_2$};
   \node[] (s7) at (5,4.5) {$\mathcal{S}$};
   \node[] (star4) at (4.5,5.5) {$*_4$};
   \node[] (c4) at (5.5,5.5) {$c_4$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

    %reduction c2 c4 c6 c3 c5
    (p1) edge node {} (s5)
         edge node {} (s8)
    (s5) edge node {} (c3)
         edge node {} (c5)
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4)

    %all
    (s9) edge node {} (s1)
         edge node {} (p1)
    (s10) edge node {} (s9)
          edge node {} (s3);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}

>>>>

%====BIG EXAMPLE
\begin{figure}[ht!]
\begin{center}
% INITIAL GRAPH
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (c0) at (0,0) {$c_0$};
   \node[] (star1) at (1,0) {$*_1$};
   \node[] (c1) at (2,0) {$c_1^*$};
   \node[] (c2) at (3,0.5) {$c_2$};
   \node[] (star4) at (3,1.5) {$*_4$};
   \node[] (c3) at (3,-0.5) {$c_3$};
   \node[] (c4) at (4,0.5) {$c_4^*$};
   \node[] (c5) at (4,-0.5) {$c_5$};
   \node[] (c6) at (5,0.5) {$c_6$};
   \node[] (c7) at (6,0) {$c_7$};
   \node[] (star8) at (7,0) {$*_8$};
   \node[] (c8) at (8,0) {$c_8^*$};

  \path[->]
    (c0) edge node {} (star1)
    (star1) edge node {} (c1)
    (c1) edge node {} (c2)
         edge node {} (c3)
         edge node {} (star4)
    (star4) edge node {} (c4)
    (c2) edge node {} (c4)
    (c4) edge node {} (c6)
    (c3) edge node {} (c5)
    (c5) edge node {} (c7)
    (c6) edge node {} (c7)
    (c7) edge node {} (star8)
    (star8) edge node {} (c8);
  \end{tikzpicture}
}
\\
% INVERSE LINE GRAPH
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c0d) at (1,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (star1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (3,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c2d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c3d) at (4,-0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (5,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c7d) at (7,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (star8d) at (8,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

  \path[->]
    (c0s) edge node [above] {$c_0$} (c0d)
    (c0d) edge node [above] {$*_1$} (star1d)
    (star1d) edge node [above] {$c_1^*$} (c1d)
    (c1d) edge node [above] {$c_2$} (c2d)
          edge node [above] {$c_3$} (c3d)
          edge [bend left=80] node [above] {$*_4$} (c2d)
    (c2d) edge node [above] {$c_4^*$} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {$c_7$} (c7d)
    (c7d) edge node [above] {$c_8$} (star8d)
    (star8d) edge node [above] {$c_8$} (c8d)
    (c3d) edge node [above] {$c_5$} (c6d);
  \end{tikzpicture}
}
\\
% TRANSFORMATIONS
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (3,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c2d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c3d) at (4,-0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (5,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

   %reduction c0 c1
   \node[] (s0) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s1) at (1,1.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,2.5) {$c_0$};
   \node[] (star1) at (1.5,2.5) {$*_1$};
   \node[] (c1) at (2,1.5) {$c_1^*$};

   %reduction c7 c8
   \node[] (s2) at (7.5,0.5) {$\mathcal{S}$};
   \node[] (s3) at (7,1.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,2.5) {$c_7$};
   \node[] (star8) at (7.5,2.5) {$*_8$};
   \node[] (c8) at (8,1.5) {$c_8$};

  \path[->]
    (c0s) edge node {} (c1d)
    (c1d) edge node [above] {$c_2$} (c2d)
          edge node [above] {$c_3$} (c3d)
          edge [bend left=80] node [above] {$*_4$} (c2d)
    (c2d) edge node [above] {$c_4^*$} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {} (c8d)
    (c3d) edge node [above] {$c_5$} (c6d)

    %reduction c0 c1
    (s0) edge node {} (s1)
         edge node {} (c1)
    (s1) edge node {} (c0)
         edge node {} (star1)
    %reduction c7 c8
    (s2) edge node {} (s3)
         edge node {} (c8)
    (s3) edge node {} (c7)
        edge node {} (star8);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (3,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c2d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (5,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

   %reduction c0 c1
   \node[] (s0) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s1) at (1,1.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,2.5) {$c_0$};
   \node[] (star1) at (1.5,2.5) {$*_1$};
   \node[] (c1) at (2,1.5) {$c_1^*$};

   %reduction c7 c8
   \node[] (s2) at (7.5,0.5) {$\mathcal{S}$};
   \node[] (s3) at (7,1.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,2.5) {$c_7$};
   \node[] (star8) at (7.5,2.5) {$*_8$};
   \node[] (c8) at (8,1.5) {$c_8$};

   %reduction c3 c5
   \node[] (s5) at (4.5,-2) {$\mathcal{S}$};
   \node[] (c3) at (4,-1) {$c_3$};
   \node[] (c5) at (5,-1) {$c_5$};

   %reduction c2 *4
   \node[] (p0) at (3.5,1) {$\mathcal{P}$};
   \node[] (c2) at (3,2) {$c_2$};
   \node[] (star4) at (4,2) {$*_4$};

  \path[->]
    (c0s) edge node {} (c1d)
    (c1d) edge node [above] {} (c2d)
    (c2d) edge node [above] {$c_4^*$} (c4d)
    (c4d) edge node [above] {$c_6$} (c6d)
    (c6d) edge node [above] {} (c8d)
    (c1d) edge [bend right] node [above] {} (c6d)

    %reduction c0 c1
    (s0) edge node {} (s1)
         edge node {} (c1)
    (s1) edge node {} (c0)
         edge node {} (star1)
    %reduction c7 c8
    (s2) edge node {} (s3)
         edge node {} (c8)
    (s3) edge node {} (c7)
        edge node {} (star8)

@@

    %reduction c2 *4
    (p0) edge node {} (c2)
         edge node {} (star4);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}

\begin{figure}[ht!]
\ContinuedFloat
\begin{center}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (3,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

   %reduction c0 c1
   \node[] (s0) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s1) at (1,1.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,2.5) {$c_0$};
   \node[] (star1) at (1.5,2.5) {$*_1$};
   \node[] (c1) at (2,1.5) {$c_1^*$};

   %reduction c7 c8
   \node[] (s2) at (7.5,0.5) {$\mathcal{S}$};
   \node[] (s3) at (7,1.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,2.5) {$c_7$};
   \node[] (star8) at (7.5,2.5) {$*_8$};
   \node[] (c8) at (8,1.5) {$c_8$};

   %reduction c3 c5
   \node[] (s5) at (4.5,-2) {$\mathcal{S}$};
   \node[] (c3) at (4,-1) {$c_3$};
   \node[] (c5) at (5,-1) {$c_5$};

   %reduction c2 c6
   \node[] (s6) at (4.5,1) {$\mathcal{S}$};
   \node[] (p0) at (3.5,2) {$\mathcal{P}$};
   \node[] (c2) at (3,3) {$c_2$};
   \node[] (star4) at (4,3) {$*_4$};
   \node[] (s7) at (5.5,2) {$\mathcal{S}$};
   \node[] (c4) at (5,3) {$c_4^*$};
   \node[] (c6) at (6,3) {$c_6$};

@@

    %reduction c0 c1
    (s0) edge node {} (s1)
         edge node {} (c1)
    (s1) edge node {} (c0)
         edge node {} (star1)
    %reduction c7 c8
    (s2) edge node {} (s3)
         edge node {} (c8)
    (s3) edge node {} (c7)
        edge node {} (star8)

@@

    %reduction c2 c6
    (s6) edge node {} (p0)
         edge node {} (s7)
    %reduction c2 *4
    (p0) edge node {} (c2)
         edge node {} (star4)
    (s7) edge node {} (c4)
         edge node {} (c6);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (3,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (7,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

   %reduction c0 c1
   \node[] (s0) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s1) at (1,1.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,2.5) {$c_0$};
   \node[] (star1) at (1.5,2.5) {$*_1$};
   \node[] (c1) at (2,1.5) {$c_1^*$};

   %reduction c7 c8
   \node[] (s2) at (7.5,0.5) {$\mathcal{S}$};
   \node[] (s3) at (7,1.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,2.5) {$c_7$};
   \node[] (star8) at (7.5,2.5) {$*_8$};
   \node[] (c8) at (8,1.5) {$c_8$};

   \node[] (p1) at (4.5,0.5) {$\mathcal{P}$};
   %reduction c3 c5
   \node[] (s5) at (5.5,1.5) {$\mathcal{S}$};
   \node[] (c3) at (5,2.5) {$c_3$};
   \node[] (c5) at (6,2.5) {$c_5$};
   %reduction c2 c6
   \node[] (s6) at (3.5,1.5) {$\mathcal{S}$};
   \node[] (p0) at (2.8,2.5) {$\mathcal{P}$};
   \node[] (c2) at (2.3,3.5) {$c_2$};
   \node[] (star4) at (3.3,3.5) {$*_4$};
   \node[] (s7) at (4.2,2.5) {$\mathcal{S}$};
   \node[] (c4) at (3.8,3.5) {$c_4^*$};
   \node[] (c6) at (4.8,3.5) {$c_6$};

@@

    %reduction c0 c1
    (s0) edge node {} (s1)
         edge node {} (c1)
    (s1) edge node {} (c0)
         edge node {} (star1)
    %reduction c7 c8
    (s2) edge node {} (s3)
         edge node {} (c8)
    (s3) edge node {} (c7)
        edge node {} (star8)

    (p1) edge node {} (s6)
         edge node {} (s5)
    %reduction c3 c5
    (s5) edge node {} (c3)
         edge node {} (c5)
    %reduction c2 c6
    (s6) edge node {} (p0)
         edge node {} (s7)
    %reduction c2 *4
    (p0) edge node {} (c2)
         edge node {} (star4)
    (s7) edge node {} (c4)
         edge node {} (c6);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (9,0) {};

   \node[] (s8) at (4.5,0.5) {$\mathcal{S}$};
   \node[] (s9) at (3,1.5) {$\mathcal{S}$};

   %reduction c0 c1
   \node[] (s0) at (1.5,2.5) {$\mathcal{S}$};
   \node[] (s1) at (1,3.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,4.5) {$c_0$};
   \node[] (star1) at (1.5,4.5) {$*_1$};
   \node[] (c1) at (2,3.5) {$c_1^*$};

   %reduction c7 c8
   \node[] (s2) at (7.5,1.5) {$\mathcal{S}$};
   \node[] (s3) at (7,2.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,3.5) {$c_7$};
   \node[] (star8) at (7.5,3.5) {$*_8$};
   \node[] (c8) at (8,2.5) {$c_8$};

   \node[] (p1) at (4.5,2.5) {$\mathcal{P}$};
   %reduction c3 c5
   \node[] (s5) at (5.5,3.5) {$\mathcal{S}$};
   \node[] (c3) at (5,4.5) {$c_3$};
   \node[] (c5) at (6,4.5) {$c_5$};
   %reduction c2 c6
   \node[] (s6) at (3.5,3.5) {$\mathcal{S}$};
   \node[] (p0) at (2.8,4.5) {$\mathcal{P}$};
   \node[] (c2) at (2.3,5.5) {$c_2$};
   \node[] (star4) at (3.3,5.5) {$*_4$};
   \node[] (s7) at (4.2,4.5) {$\mathcal{S}$};
   \node[] (c4) at (3.8,5.5) {$c_4^*$};
   \node[] (c6) at (4.8,5.5) {$c_6$};

@@

    (s8) edge node {} (s9)
         edge node {} (s2)
    (s9) edge node {} (p1)
         edge node {} (s0)

    %reduction c0 c1
    (s0) edge node {} (s1)
         edge node {} (c1)
    (s1) edge node {} (c0)
         edge node {} (star1)
    %reduction c7 c8
    (s2) edge node {} (s3)
         edge node {} (c8)
    (s3) edge node {} (c7)
        edge node {} (star8)

    (p1) edge node {} (s6)
         edge node {} (s5)
    %reduction c3 c5
    (s5) edge node {} (c3)
         edge node {} (c5)
    %reduction c2 c6
    (s6) edge node {} (p0)
         edge node {} (s7)
    %reduction c2 *4
    (p0) edge node {} (c2)
         edge node {} (star4)
    (s7) edge node {} (c4)
         edge node {} (c6);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}
